Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-03-16 paper/paper.tex
removed the now redundant other-mnist-like section; moved cplx-backprop and linear operator to the back

Shaded horizontal bands reflect the spread of the performance of the uncompressed network
after ``dense'' stage. Each point represents a precision-compression value attained by the
network after ``fine-tune'' stage. The end of each point's tail represents the performance
gain or loss from running the ``fine-tune'' stage.
%
We make a couple of observations based on the results of these plots. First, \texttt{fft}
features perform on par with raw colour channel data in the convolutional networks across most
compression rates, but require high compression rate to make wide shallow dense network work
as well. The upward trend manifests itself in MNIST and Fashion MNIST experiments as well
(see appendix~\ref{sub:other_mnist_like_datasets}). Finally, overall $\cplx$ variational
dropout methods seem to compress networks adequately well without much loss in performance.

@@

\subsection{Other MNIST-like datasets} % (fold)
\label{sub:other_mnist_like_datasets}

We provide the figures of the MNIST-like experiments, omitted from the main paper
due to size limitations.

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off on the letters part of the Fashion MNIST dataset.
    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
  }
  \label{fig:mnist-like__trade-off__fashionmnist}
\end{figure}

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off on the letters part of the MNIST dataset.
    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
  }
  \label{fig:mnist-like__trade-off__mnist}
\end{figure}

% subsection other_mnist_like_datasets (end)

>>>>

Shaded horizontal bands reflect the spread of the performance of the uncompressed network
after ``dense'' stage. Each point represents a precision-compression value attained by the
network after ``fine-tune'' stage. The end of each point's tail represents the performance
gain or loss from running the ``fine-tune'' stage.
%
We make a couple of observations based on the results of these plots. First, \texttt{fft}
features perform on par with raw colour channel data in the convolutional networks across most
compression rates, but require high compression rate to make wide shallow dense network work
as well. The upward trend manifests itself in MNIST and Fashion MNIST experiments as well
(see appendix~\ref{sub:mnist_like_experiments}). Finally, overall $\cplx$ variational dropout
methods seem to compress networks adequately well without much loss in performance.

@@
